\TheTitle

### 2016-04-25 linvis.tex

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/gitk.png}
        \caption{A sample DAG view of commits from Linux in gitk. Commits point towards their ancestors, and there is no clear indication of the way the travel
          to reach Master. In fact, neither gitk nor git is capable of showing what commits were done in master.}
        \label{fig:gitk}
\end{figure}

@@

Our goal was to build a tool to enable maintainers to effectively navigate and browse
the changes performed to the kernel over the period of a release.
Achieving this goal includes removing information that does not pertain to the area
of the kernel that the user is interested in. In figure \ref{fig:dag_view} and
figure \ref{fig:tree_view} we can visually compare the results returned from gitk
and our tool for the top-level merge ``042dd60ca6dec9a02cefa8edd67de386e35755d6''
from kernel version 3.10. Note first that gitk has no way to show that this is a merge into Master.

The log information to this merge-commit in both of these
figures is identical, but the presentation drastically changes our ability to
comprehend what we are seeing. The primary difference is the removal of irrelevant
information. In gitk (\ref{fig:dag_view}), the visualization results include commits
and merges from other components of the kernel, while our tool (\ref{fig:tree_view})
only includes the results that are specific to the component of the kernel that we
are interested in.

@@

\evantodo{Move related work to the end, try to match the text of the paper to my intro}

To our knowledge, we know of no git repository visualization tool that builds
a tree that maps the path commits follow to master
from the DAG provided by git. This may be because more information is required
to generate the tree-model than what is stored by git. % Git uses a DAG model, which
% enables history-altering actions, like rebases to occur, whereas older tools like
% CVS and svn construct trees\cite{CVS2008} but do not work with history-altering
% actions.

% A server must sit and monitor the git repository as it changes over time to record
% the changes to history. Many of the visualization tools are designed for a
% general-purpose approach, where any repository is directly usable without additional
% information. Polling for this additional information makes the visualizer specific
to a repository or project.

\subsection{Other Visualizers}

Gitk, Gitg, and other similar git repository visualization tools use the DAG as the
central organization model. This model is sufficient for smaller projects, providing
meaningful information; however, in larger projects, like the Linux kernel, the
branches become too tangled and too deep to derive any meaning from the DAG. Users
can interact with the DAG by going to the previous commit in the chain or jumping to
the parent merge. Given the direction that each node in the DAG has (pointing to its parent)
it can be assumed that tools that exploit the DAG (such as gitk and similar tools) are designed for users
working from a given commit towards the past. Working in the opposite direction is hard, since merge commits provide multiple paths towards the present, with no
way to distinguish which path is the one used by the current commit to be merged into master.

Furthermore, the DAG model is only able to provide file-level information for
commits. It is unable to quickly aggregate the file data over all commits that
are part of a merge. If a user would like to view what files were edited at a merge,
they must manually aggregate this information by hand. While some merges are
relatively small, containing less than 10 commits, other merges are large,
containing over 1500 edited files, as in the case of commit \textit{73287a4}. This
issue is important for authorship and licensing. A merge can only show one author,
the contributor making the merge, but does not show who wrote the commits contained
within that merge.

%% Check for papers if they exist
%% This tool isn't specifically designed for showing Linux

\subsection{Treemap visualizer}

University of Maryland presented a treemap visualization
tool\footnote{\url{https://www.cs.umd.edu/hcil/millionvis/Treemap_Visualization_of_the_Linux_Kernel_2_5_33.html}},
pictured in figure \ref{fig:treemap}, for displaying the file structure of a given
version of the kernel. Treemaps are good for visualizing the topology of shallow,
wide trees, making it a good candidate for displaying file systems. Treemaps are
limited in what information can be displayed. The information within the treemap
does not provide clear insight into what changes were made to the files in the given
release. It only provides information on where the file is located within the file
system; they do not provide temporal information. File systems and the merge
tree of the kernel share many similarities, in both cases, they represent trees that
are wide and shallow, suggesting that a treemap could potentially work to visualize
the commit and merge structure of the kernel.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/kernel-files.png}
        \caption{Treemap of Linux 2.5.33 file structure}
        \label{fig:treemap}
\end{figure}

The treemap is unable to take into account multiple commits behind the same merge
with the same log preview message. Commits and merges have an ordering in which they
were added to the kernel, which cannot be represented by a treemap, but is important
and can be used to assist in building the tree.

The treemap is also designed for working with data of differing types. In the
filesystem, there are many kinds of files. There are text files, scripts, images,
binary files, and other types. These can be given colours making differences stand
out. There is no obvious way to assign meaningful types to the commits such that all
the commits within a given merge do not have the same colour, although a user
could be given a controller to colour by author or number of files edited.

Finally, the treemap does not provide any additional information about the
contents of each cell, only that the cell exists and where it exists in the
tree. The user is unable to see their current position within the map, or if we
assume that their current position is the largest surrounding box, they can
no longer see how their current position interacts with the rest of the
system.
%% https://www.cs.umd.edu/hcil/millionvis/Treemap_Visualization_of_the_Linux_Kernel_2_5_33.html
%% Find paper for this maybe?

\subsection{List viewer}

Moghaddam designed a web-based visualization
tool\footnote{\url{http://web.uvic.ca/~arasbm/gitVisualizations/linuxRGraph.html}}
displaying the chain of merges into the kernel. There is no information on what
commits are within a given merge, or what files were edited. The visualization
tool provides information about who authored the commit and when it was
authored. We can see the visualization tool in figure \ref{fig:listviewer}
displaying a part of the kernel commit information, from commit ``26b23ac''
according to the tool.

%% http://web.uvic.ca/~arasbm/gitVisualizations/linuxRGraph.html
%% Find paper for this maybe?

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/gitvis.png}
        \caption{List Viewer}
        \label{fig:listviewer}
\end{figure}

>>>>

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/gitk.png}
        \caption{A sample DAG view of commits from Linux in Gitk. Commits point towards their ancestors, and there is no clear indication of the way the travel
          to reach Master. In fact, neither Gitk nor git is capable of showing what commits were done in master.}
        \label{fig:gitk}
\end{figure}

@@

Our goal was to build a tool to enable maintainers to effectively navigate and browse
the changes performed to the kernel over the period of a release.
Achieving this goal includes removing information that does not pertain to the area
of the kernel that the user is interested in. In figure \ref{fig:dag_view} and
figure \ref{fig:tree_view} we can visually compare the results returned from Gitk
and our tool for the top-level merge ``042dd60ca6dec9a02cefa8edd67de386e35755d6''
from kernel version 3.10. Note first that Gitk has no way to show that this is a merge into Master.

The log information to this merge-commit in both of these
figures is identical, but the presentation drastically changes our ability to
comprehend what we are seeing. The primary difference is the removal of irrelevant
information. In Gitk (\ref{fig:dag_view}), the visualization results include commits
and merges from other components of the kernel, while our tool (\ref{fig:tree_view})
only includes the results that are specific to the component of the kernel that we
are interested in.

@@

Version control systems monitor the development lifetime of software projects. This
makes the version control system vital in providing information about how a software
project is being developed. To our knowledge, we know of no git repository
visualization tool that builds a tree that maps the path a commit follows to the
master branch from the DAG provided by git. This may be because more information is
required to generate the tree-model than what is stored by git. However, there has
been a lot of work in providing visualizations of various repositories.

Many of the tools work to address the issues of communication between developers and
inter-team collaboration. Codebook uses a mining technique to determine the
developer of a piece of code, the program manager who wrote the specification for
the code, and the program managers and developers on the team who were working
together\cite{Begel2010}. This is designed to help collaboration between developers
on a project while the project is being developed.  In maintaining the code, the
code has already been written, the original developer many not have seen this piece
of code in years, and will most likely have moved to another problem. If the
maintainer is pulling from a part of the kernel that has been recently updated, in
the event of a zero-day attack for instance, the information about who is developing
that portion of the kernel is of use; however, if the maintainer is pulling from
sections that are older, then the maintainer must be able to understand the code
using the provided tools, not the original developer.

Hipikat is another tool with a focus on communication issues between developers. It
is designed for non-collocated teams, helping new developers understand design
decisions of the system \cite{Cubranic2005}. It records artifacts about the project
to build a "memory" of the project development that new users can work with to
understand where and how to make modifications in large projects. The artifacts are
recorded using tools like bugzilla and CVS. Such a tool could prove useful in
understanding the changes between a maintainer's current version of an older kernel
and the changes being made to the current master version of the kernel.

These tools work toward assisting the communications between developers and
providing a summary of the project. Our goal includes providing a visual summary of
the topology of the repository, as well as providing a summary of the changes made
at a location within the repository. EPOSee, Gource, and Gitk are all tools designed
for visualizing various aspects of repositories.

EPOSee is a tool for visualizing changes that often happen simultaneously in a
commit or as a sequence of events \cite{Burch2005}. It produces visualizations about
the confidence that changes are made either together or sequentially. For instance,
changes in the header file may also indicate that a change was made in the
implementation file. The visualization tool is designed to visualize implicit rules
about the order of operations on various files, if too many outliers are detected,
the project manager may want to restructure the project.  While this is useful for
new projects, the development model of the Linux kernel is already structured and is
unlikely to change without good reasons behind it.

Gource is a tool for providing an interactive timelapse of the state of a
repository\cite{Caudwell2010}. In the timelapse, it shows who contributes and what
type of contribution a developer is making. These contribution types are one of,
adding a file, removing a file, and changing a file. While the timelapse is
interesting to watch, it does not provide any additional explanation of the changes
actually being made, only the frequency that they are being made and who is making
them.

The current industry standard tool for git repository visualization is Gitk. The
Gitk interface is built around the central DAG viewer. The DAG view displays the
commits on their respective branches, the author of the commit or merge, and the
date the commit or merge was authored. A user can select a single merge or commit
to view additional information. For both merges and commits, Gitk will present the
user with the git log. If the user selected a commit, Gitk will also present the
user with the patch information and the names of the files edited. Gitk is unable to
provide the patches and filenames information in merges, as it is unable to
aggregate commit information in merges.
